MINOS Handover Plots

### 2024-06-26 minos/outcomes/ChildPovReduction_Combined.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

```{r "Data", include=FALSE}
scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

SF12_change_treated(scen = 'ChildPovertyReductionRELATIVE_2')
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = 'ChildPovertyReductionABSOLUTE')
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = 'ChildPovertyReductionABSOLUTE')
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = 'ChildPovertyReductionABSOLUTE')
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = 'ChildPovertyReductionABSOLUTE')
```

@@

SF12_change_treated(scen = 'ChildPovertyReductionABSOLUTE')
```

>>>>

```{r "Data", include=FALSE}
scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.rel <- 'ChildPovertyReductionRELATIVE_2'
scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
scen.abs <- 'ChildPovertyReductionABSOLUTE'
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen.rel)
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = scen.rel)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen.rel)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = scen.rel)
```

@@

SF12_change_treated(scen = scen.rel)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen.abs)
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = scen.abs)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen.abs)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = scen.abs)
```

@@

SF12_change_treated(scen = scen.abs)
```

### 2024-06-26 minos/outcomes/child_poverty_reduction_vis.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)

@@

```{r}
# base.2021 <- base.dat %>%
#   filter(time == 2021)
# 
# mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
# rel.pov.threshold <- mean.hh_income * 0.6
# 
# print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
# rm(base.2021, mean.hh_income, rel.pov.threshold)
```

@@

```{r}
# threshold <- base.dat %>%
#   select(time, weight, hh_income) %>%
#   group_by(time) %>%
#   summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))
# 
# ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
#   geom_col() +
#   geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
#   labs(title = 'Relative poverty threshold over time') +
#   xlab('Year') +
#   ylab('Threshold')
```

@@

```{r}
# sample_information(int1.rel, target.year = 2030)
```

@@

```{r}
# full.sample.change.SF12(base.dat, int1.rel)
# all.families.change.SF12(base.dat, int1.rel)
# poverty.families.change.SF12.variable(base.dat, int1.rel, threshold)
# treatment.on.treated.change.SF12(base.dat, int1.rel)
```

>>>>

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)

@@

```{r}
base.2021 <- base.dat %>%
  filter(time == 2020)

mean.hh_income <- weighted.mean(base.2021$hh_income, w = base.2021$weight)
rel.pov.threshold <- mean.hh_income * 0.6

print(paste0("Relative poverty threshold in 2020: ", rel.pov.threshold))
rm(base.2021, mean.hh_income, rel.pov.threshold)
```

@@

```{r}
threshold <- base.dat %>%
  select(time, weight, hh_income) %>%
  group_by(time) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = threshold$poverty_threshold[threshold$time == 2020], linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

@@

```{r}
sample_information(int1.rel, target.year = 2030)
```

@@

```{r}
full.sample.change.SF12(base.dat, int1.rel)
all.families.change.SF12(base.dat, int1.rel)
poverty.families.change.SF12.variable(base.dat, int1.rel, threshold)
treatment.on.treated.change.SF12(base.dat, int1.rel)
```

### 2024-06-26 minos/validation/handovers.Rmd
Switching SF_12 model back to LMM, and some small adjustments to hh_income_diff model. Also updated some summary targets for a bit of brevity

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
handover_boxplots(raw.dat, base.dat, 'council_tax')
handover_lineplots(raw.dat, base.dat, "council_tax")
```

@@

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

@@

spaghetti_plot(base.inc, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")
# 
# raw.sf12 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# # merge before plot
# sf12 <- rbind(raw.sf12, base.sf12)
# 
# # Now plot
# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_smooth() +
#   #geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
#   xlab('Year') +
#   ylab('SF12')
# 
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.sf12.2 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12.2 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
# 
# # Now plot
# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
#   xlab('Year') +
#   ylab('SF12')
# 
# if (shall.we.save) {
#   ggsave(filename = 'SF12_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

@@

>>>>

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")

handover_boxplots(raw.dat, base.dat, 'hh_income_diff')
handover_lineplots(raw.dat, base.dat, "hh_income_diff")
# handover_boxplots(raw.dat, base.dat, 'council_tax')
# handover_lineplots(raw.dat, base.dat, "council_tax")

handover_boxplots(base.dat, base.dat, 'hh_income_diff')
handover_lineplots(base.dat, base.dat, "hh_income_diff")
```

@@

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income, hh_income_diff)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income, hh_income_diff)

@@

spaghetti_plot(income.spag.sample, 'hh_income_diff',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(income.spag.sample, 'hh_income_diff',
               save = shall.we.save,
               save.path = save.path)

# spaghetti_plot(base.inc, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)

@@

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")

handover_boxplots(raw.dat, base.dat, 'SF_12_diff')
handover_lineplots(raw.dat, base.dat, "SF_12_diff")

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)

@@

spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)
